Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-18 VMCAI-revised-version/final.tex
up

Continuous VASS~\cite{DBLP:journals/tocl/BlondinFHH17}, or $\mathds{Q}^d$-VASS are a relaxation of classical discrete VASS in which transitions can be fired a fractional number of times, and consequently counters may contain a fractional number of tokens.

>>>>

$\mathds{Q}^d$-VASS~\cite{DBLP:journals/tocl/BlondinFHH17} (or continuous VASS) are a relaxation of classical discrete $d$-VASS in which transitions can be fired a fractional number of times, and consequently counters may contain a fractional number of tokens.
